### 2015-03-04 appendices.tex
added some database diagrams single space the references
some minor typos and proof reading
working on case study - quality

\section{Detailed Steps of the SDLC}
\label{app:detailedSDLC}

    Often times the SDLC contains more than the 5 basic steps of requirements, design,
    implementation, testing, and  deployment/maintenance.  Those are the high-level
    phases, but many steps are required to complete each phase.  The following list
    provides a more detailed version of what needs to be accomplished in the 
    entire life cycle of software development. These steps do not need 
    to occur in a sequential fashion.

@@

%% set appendix to single space for th source code
\linespread{1.0}

@@

\subsection{R CODE - QUALITY}

>>>>

\section{DETAILED STEPS OF THE SDLC}
\label{app:detailedSDLC}

    Often times the SDLC contains more than the 5 basic steps of requirements, design,
    implementation, testing, and  deployment/maintenance.  Those are the high-level
    phases, but many steps are required to complete each phase.  The following list
    provides a more detailed list of what needs to be accomplished in the 
    entire life cycle of software development. These steps do not need 
    to occur in a sequential fashion.

@@

\section{SDLC-AE SOURCE CODE}

%% set appendix to single space for the source code
\linespread{1.0}

@@

    \subsection{QUALITY HISTORICAL SOURCE CODE AND ANALYSIS}
    \label{app:quality-history}
        \lstinputlisting[language=R]{source/quality.R}
        The source code for the selected baseline quality function
        can be seen above. The output for the linear model can be seen below.
        \lstinputlisting{source/quality_output.txt}

        Some diagnostic plots for the baseline quality function
        can be seen in Figure \ref{fig:quality-diag}.  The normal probability plot,
        a.k.a. QQ Plot, shows the errors are not exactly normally distributed, but
        the baseline quality function had good predictive power as shown by the
        high $R^2$. The fitted versus
        residuals plot indicates a lack of heteroscedasticity.  
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/quality_diag.png}
            \caption{QUALITY DIAGNOSTIC PLOTS}
            \label{fig:quality-diag}
        \end{figure}

        Figure \ref{fig:quality-pairs} shows the presence of some
        possible multicolinearity.  As a result, ridge regression
        was used to create a model, but the results were very similar
        to the original baseline quality function. Therefore,
        ridge regression was not chosen. 
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/quality_pairs.png}
            \caption{QUALITY PAIRS PLOT OF INDEPENDENT VARIABLES}
            \label{fig:quality-pairs}
        \end{figure}

### 2015-03-04 paper_70_case-study.tex
working on case study - quality

    \subsection{WITH HISTORICAL DATA}
        After the data has been collected, the raw data can be stored in the SDLC
        if desired.  Then scores for each of the 4 elements can be calculated.
        \subsubsection{QUALITY}
            The first step to dealing with the quality data is a quick
            analysis of the data.  Table \ref{tab:quality_desc} provides
            some descriptive statistics for the quality data.

@@

            Notice, the data for quality goes from October 2007 to January 2015
            and contains 985 observations.
            This is important because historical data can be used to create the
            baseline quality function.  All quality for the years 2007 through 2013
            will be used as historical data for the purposes of creating
            the baseline quality function.  Once the historical data is separated,
            it results in 799 observations to be used for creating the baseline
            quality function.

>>>>

    \subsection{WITH HISTORICAL DATA}
        After the data has been collected, the raw data can be stored in the SDLC
        if desired.  Then scores for each of the 4 elements can be calculated.
        For this example, the value of $k$ will be 100 and the time
        frequency will be monthly.  Thus, scores will fall
        in the range $[-100,100]$.
        \subsubsection{QUALITY}
            The first step to dealing with the quality data is a quick
            analysis of the data.  Table \ref{tab:quality_desc} provides
            some descriptive statistics for the quality data.  Testing hours
            were not capture but they are optional, so the analysis can 
            continue.

@@

            Notice, the data for quality goes from October 2007 to January 2015
            and contains 985 observations.
            This is important because historical data can be used to create the
            baseline quality function.  All quality for the years 2007 through 
            the end of 2013
            will be used as historical data for the purposes of creating
            the baseline quality function.  Once the historical data is separated,
            it results in 799 observations to be used for creating the baseline
            quality function.  Figure \ref{fig:quality-plots1} shows scatterplots
            of PROD\_DFTS versus the independent variables of DEV\_EFF, SIT\_DFTS,
            and UAT\_DFTS.  It can be seen that some correlations exist between
            the variables.

            \begin{figure}[ht]
                \centering
                \includegraphics[scale=.3]{images/quality_plots1.png}
                \caption{QUALITY DATA PLOTS: DEPENDENT VS. INDEPENDENT VARIABLES}
                \label{fig:quality-plots1}
            \end{figure}

            Figure \ref{fig:quality-plots1} also shows the presence of a possible outlier
            with 1216 PROD\_DFTS.  That data point is dropped for the remaining analysis.
            At this point, a simple linear regression model can be fit to the remaining
            798 observations. At this point, no transformations have been performed
            on the data.  The linear regression model yields all 3 independent
            variables as significant and an overall $R^2 = .72$.  The source
            code and some further analysis can be found in Appendix 
            \ref{app:quality-history}. It appears to 
            be a good fit and thus all Application IDs will have the same baseline
            quality function.  Therefore, $f$ does not need a subscript, and $f$
            can be seen below.

            \[
                f = 5.92+ 0.035 \cdot DEV\_EFF - 0.36 \cdot SIT\_DFTS + 1.05 \cdot UAT\_DFTS
            \]

            Now that $f$ has been determined, the quality scores for each
            application can be calculated for all the months beyond 2013.
